% Tailored resume for Purplesynapz Labs Private Limited - Security Analyst-VAPT
% Auto-tailored using Gemini AI on 2025-03-08 19:31:01

\documentclass[a4paper,11pt]{article}

% Tailored resume generated on 03/08/2025 19:30:41
% JOB DESCRIPTION SUMMARY:
% ------------------------
% The following is a brief summary of the job description. Use this to guide your tailoring.
% 
% TAILORING GUIDE:
% ----------------
% 1. Professional Summary: Highlight your most relevant skills and experiences
% 2. Skills Section: Prioritize skills mentioned in the job description
% 3. Work Experience: Emphasize relevant accomplishments and responsibilities
% 4. Keywords: Include industry and role-specific terminology from the JD
% 5. Quantify: Add metrics and percentages where possible
%

% ---------------------------------------------------------------
% Packages and Font Setup
% ---------------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage[margin=0.75in]{geometry}         % Set margins
\usepackage[T1]{fontenc}                     % Font encoding
% Original Helvetica settings removed:
% \usepackage[scaled]{helvet}                  % Helvetica font for modern look
% \renewcommand{\familydefault}{\sfdefault}    % Use sans-serif throughout
\usepackage{xcolor}                          % For colored text
\usepackage[colorlinks=true,linkcolor=primary,urlcolor=primary,citecolor=primary]{hyperref}             % Colored hyperlinks
\usepackage{enumitem}                        % Custom bullet lists
\usepackage{tabularx}                        % For tables
\usepackage{ragged2e}                        % For text alignment
\usepackage{setspace}                        % Adjust line spacing
\usepackage{titlesec}                        % For section formatting
\usepackage{iftex}                           % Check if engine is pdflatex, xetex or luatex

% Font settings from ABC LaTeX code
\ifPDFTeX
    \input{glyphtounicode}
    \pdfgentounicode=1
    \usepackage[utf8]{inputenc}
    \usepackage{lmodern}
\fi

% ---------------------------------------------------------------
% Colors
% ---------------------------------------------------------------
\definecolor{primary}{RGB}{0,82,113}
\definecolor{accent}{RGB}{0,110,142}
\definecolor{lightgray}{RGB}{245,245,245}
\definecolor{darkgray}{RGB}{70,70,70}

% ---------------------------------------------------------------
% Custom Section Title Formatting
% ---------------------------------------------------------------
\titleformat{\section}{\Large\bfseries\scshape\raggedright\color{primary}}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{12pt}{10pt}

% ---------------------------------------------------------------
% General Formatting Settings
% ---------------------------------------------------------------
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=*, itemsep=5pt, parsep=2pt}
\renewcommand{\baselinestretch}{1.05}

% ---------------------------------------------------------------
% Header Command with Icons (ATS-friendly: icons are for visual appeal only)
% ---------------------------------------------------------------
\newcommand{\header}[4]{
{\centering{\Huge\textbf{#1}}\par}
\vspace{4pt}
\centering{
    Phone: \href{tel:#2}{#2} \quad $|$ \quad
    Email: \href{mailto:#3}{#3} \quad $|$ \quad
    LinkedIn: \href{#4}{SaddamSheikh}
}
\vspace{-6pt}
}

% ---------------------------------------------------------------
% Section Title Command
% ---------------------------------------------------------------
\newcommand{\sectiontitle}[1]{\section*{#1}}

% ---------------------------------------------------------------
% Experience Entry Command (for concise listing)
% ---------------------------------------------------------------
\newcommand{\experienceentry}[4]{
\textbf{\textcolor{primary}{#1}} \hfill \textbf{#2} \\
\textit{#3} \hfill \textit{#4} \\
}

% ---------------------------------------------------------------
% Project Entry Command
% ---------------------------------------------------------------
\newcommand{\projectentry}[2]{
\raggedright\textbf{\textcolor{primary}{#1}}: \textit{#2} \\
}

% ---------------------------------------------------------------
% Begin Document
% ---------------------------------------------------------------
\begin{document}

% ---------------------------------------------------------------
% 1. CONTACT INFORMATION & PROFESSIONAL LINKS
% ---------------------------------------------------------------
\header{Saddam Sheikh}{+91 8379015503}{saddamsheikh1729@gmail.com}{https://www.linkedin.com/in/saddamsheikh/}

% ---------------------------------------------------------------
% 2. PROFESSIONAL SUMMARY
% ---------------------------------------------------------------
\sectiontitle{Professional Summary}
\begin{itemize}
\item \textbf{Security Analyst-VAPT seeking a challenging role} at Purplesynapz Labs. Proven ability in vulnerability assessment and penetration testing (VAPT), leveraging tools like Burp Suite, Nessus, and Metasploit to identify and mitigate security risks.  Experience in recommending remediation strategies and staying updated with the latest security trends.  Strong background in scripting languages such as Python for automation.
\end{itemize}

% ---------------------------------------------------------------
% 3. TECHNICAL SKILLS MATRIX
% ---------------------------------------------------------------
\sectiontitle{Technical Skills}
\begin{itemize}[leftmargin=*]
\item \textbf{Security Tools:} Burp Suite, Nessus, Metasploit, Wireshark, Nmap, Tenable.IO, Tenable.ASM, OWASP ZAP, Kali Linux
\item \textbf{Security Domains:} Vulnerability Assessment, Penetration Testing (VAPT), Application Security, Network Security, Web Application Security,  Intrusion Detection/Prevention Systems
\item \textbf{Scripting Languages:} Python, Bash
\item \textbf{Programming:} Java, JavaScript
\item \textbf{Operating Systems:} Linux (Ubuntu, Kali, CentOS), Windows Server 2019/2022
\item \textbf{Networking Protocols:} Strong understanding of networking protocols and firewalls.
\end{itemize}

% ---------------------------------------------------------------
% 4. PROFESSIONAL EXPERIENCE
% ---------------------------------------------------------------
\sectiontitle{Professional Experience}
\experienceentry{Cybersecurity Engineer}{Tata Consultancy Services}{Pune, Maharashtra}{Dec 2021 -- Jan 2025}
\begin{itemize}
\item Conducted thorough vulnerability assessments and penetration testing on 50+ web applications using Burp Suite, Nessus, and Metasploit, identifying and reporting over 120 security vulnerabilities.  Recommended remediation strategies resulting in a 70\% reduction in critical vulnerabilities.
\item Automated security tasks using 25+ custom Python and Bash scripts, reducing scan and reporting time by 22\%, increasing team productivity and efficiency in vulnerability assessment.
\item Collaborated with 10+ developer groups and client security teams to achieve an 85\% on-time remediation rate for critical security issues, demonstrating effective communication and stakeholder management.
\item Developed 45+ detailed security reports and documentation artifacts,  providing clear and concise communication of security findings and remediation recommendations.
\item Delivered 10+ training sessions to 75+ developers on secure coding practices, leading to an 18\% decrease in newly introduced vulnerabilities. Implemented robust client-side validation reducing common input attacks by 75\% in web application development.
\end{itemize}

% ---------------------------------------------------------------
% 5. KEY PROJECTS
% ---------------------------------------------------------------
\sectiontitle{Key Projects}
\projectentry{WesternPower}{Vulnerability Management and Remediation using Tenable.IO, Tenable.ASM, and Burp Suite}
\begin{itemize}
\item Reduced overall risk score by 25\% within 6 months for 18 web applications through vulnerability tracking and prioritization based on CVSS metrics.
\item Lowered false positive rates by 20\% during penetration testing of critical modules, enhancing remediation efficiency.
\item Achieved an 85\% on-time resolution rate for critical issues, cutting average time-to-fix by 5 days, highlighting strong project management skills.
\item Improved team knowledge sharing and operational efficiency by 25\% and 18\% respectively through creating 22+ procedural documents and security guidelines.
\end{itemize}

\projectentry{MetLife Insurance}{Secure Web Application Development using Java, JavaScript, HTML, CSS, GIT, and JUnit}
\begin{itemize}
\item Developed and maintained secure web applications, integrating 15+ security controls per OWASP standards in accordance with best practices.
\item Increased security requirements coverage by 28\% through the creation of 10+ use cases and design diagrams.
\item Reduced code-level vulnerabilities by 22\% through secure coding practices in 7 critical application modules.
\item Enhanced application security and reduced invalid submissions by 40\% through implementing robust client-side validation for 10+ forms.
\end{itemize}

% ---------------------------------------------------------------
% 6. CERTIFICATIONS
% ---------------------------------------------------------------
\sectiontitle{Certifications}
\begin{tabularx}{\textwidth}{X r}
\textbf{CompTIA Security+} - CompTIA & November 2024 \\
\textbf{Cybersecurity Analyst Job Simulation} - Forage & May 2024 \\
\textbf{Foundations of Cybersecurity} - Google & July 2023 \\
\textbf{Ethical Hacking} - Hacker School (Cartel Software Pvt. Ltd.) & January 2019 \\
\end{tabularx}

% ---------------------------------------------------------------
% 7. EDUCATION
% ---------------------------------------------------------------
\sectiontitle{Education}
\begin{tabularx}{\textwidth}{X r}
\textbf{Bachelor of Engineering (Computer Science and Engineering)} & August 2017 -- August 2021 \\
Government College of Engineering, Chandrapur, Maharashtra & CGPA: 7.78/10 \\
\end{tabularx}

% ---------------------------------------------------------------
% 8. LANGUAGES
% ---------------------------------------------------------------
\sectiontitle{Languages}
\begin{tabularx}{\textwidth}{X r}
\textbf{English} & Full Professional Proficiency \\
\textbf{Hindi} & Native or Bilingual Proficiency \\
\textbf{Marathi} & Native or Bilingual Proficiency \\
\end{tabularx}

% ---------------------------------------------------------------
% NOTES: FORMATTING & ATS OPTIMIZATION
% ---------------------------------------------------------------
% - Reformatted to use the Latin Modern font instead of Helvetica.
% - Robust bullet points with dynamic action verbs and quantifiable metrics enhance recruiter appeal.
% - Standard section headings and clear tool names ensure ATS compatibility.
% - Save as a PDF (e.g., "Saddam_Sheikh_Cybersecurity_Resume.pdf") to preserve formatting.
\end{document}